---
title: "Описание данных"
output:
  html_document:
    code_download: yes
    fontsize: 8pt
    highlight: textmate
    number_sections: no
    theme: flatly
    toc: yes
    toc_float:
      collapsed: no
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(dplyr)
library(data.table)
library(lme4)
library(ggplot2)
library(parameters)
library(rstatix)
library(blmeco)
library(arm) # for display()

remove_outliers <- function(x, na.rm = TRUE, ...) {
  qnt <- quantile(x, probs=c(.25, .75), na.rm = na.rm, ...)
  H <- 1.5 * IQR(x, na.rm = na.rm)
  y <- x
  y[x < (qnt[1] - H)] <- NA
  y[x > (qnt[2] + H)] <- NA
  y
}

```



```{r, include=FALSE}
wd <- getwd()
students <- fread("../data/students.csv") %>% group_by(course_id) %>%
  mutate(vis_p = remove_outliers(vis_p))  
students$vis_b <-factor(students$vis_b)
students$spec_b <-factor(students$spec_b)

assignments <- fread("unzip -cq ../data/assignments.zip")  %>% group_by(course_name)   %>% mutate(course_item_type_desc = factor(course_item_type_desc)) %>% ungroup()

courses <- fread("../data/courses.csv")%>%
  mutate(passing_rate = passing_rate * 100, student_vis_rate = round(vis_learner_b/student_n, digits = 2), student_vis_mean = round(student_vis_mean, digits = 2))

```

## 1. Descriptive statistics

Number of courses:

```{r}
nrow(courses)
```

Number of students enrolled:

```{r}
sum(courses$enrolled)
```

Number of students passed the course:

```{r}
pass <- sum(courses$student_n)
pass
```


Number of courses with programming assignments and not:

```{r}
table(courses$is_prog_b)
```

Number of courses within specialization and not:

```{r}
table(courses$spec_b)
```

Number of courses on Russian and English:

```{r}
e <-sum(grepl('^[^\x20-\x7F]', courses$course_name))
c(e, nrow(courses) -e)
```

Number of finished programming assignments and quizzes:

```{r}
table(assignments$course_item_type_desc)
```

Number of programming assignments and quizzes:

```{r}
assignments %>% distinct(course_item_id, .keep_all=TRUE) %>% group_by(course_item_type_desc) %>% summarize(n = n())
```

Status of first attempt for programming assignments and quizzes:

```{r}
table(assignments$first_attempt)
```


Number of questions and anwers on forum:

```{r}
sum(courses$q_learner)
#sum(students$q_n)
sum(courses$ans_learner)
#sum(students$ans_n)
```

Number of students posted anything on forum:

```{r}
q <- students %>% filter(q_n != 0) %>% group_by(course_id, hse_user_id) %>% nrow()
a <- students %>% filter(ans_n != 0) %>% group_by(course_id, hse_user_id) %>% nrow()
t <- students %>% filter(ans_n != 0 || q_n != 0) %>% group_by(course_id, hse_user_id) %>% nrow()
q
a
t
```

Proportion of students posted anything on forum:

```{r}
round(q / pass, digits = 2)
round(a / pass, digits = 2)
round(t / pass, digits = 2)
```
Number of students visited a forum:

```{r}
v <- students %>% filter(vis_b != 0) %>% group_by(course_id, hse_user_id) %>% nrow()
v
```


The proportion of students visited forum:

```{r}
round(v / pass, digits = 2)
```
The proportion of students posted anything among those who visited a forum:

```{r}
round(v / pass, digits = 2) / round(t / pass, digits = 2) 
```

## 2. To check
Number of passed students on the least and the most popular courses

```{r}
min(courses$student_n)
max(courses$student_n)
```

```{r}
hist(courses$student_n, breaks = 60)
table(courses$student_n)
summary(courses$student_n)
```

Number of programming assignments in programming courses:

```{r}
#  и еще число всех заданий
a <- courses %>% dplyr::select(is_prog_n, course_slug) %>% group_by(course_slug) %>% 
  summarize(prog_n_courses = sum(is_prog_n, na.rm = TRUE)) %>%  filter(prog_n_courses != 0) %>% arrange(course_slug) 
b <- assignments %>% group_by(course_name) %>% dplyr::select(course_item_type_desc, course_item_name) %>% rename(course_slug = course_name)   %>% 
    filter(course_item_type_desc == "programming") %>% summarize(prog_n_ass = n_distinct(course_item_name)) %>% arrange(course_slug)
q <- assignments %>% group_by(course_name) %>% dplyr::select(course_item_type_desc, course_item_name) %>% rename(course_slug = course_name)   %>% 
    filter(course_item_type_desc == "quiz") %>% summarize(quiz_n_ass = n_distinct(course_item_name)) %>% arrange(course_slug)
```

```{r}
#  разница возникает из-за того что во assignments  - только оцениваемые задания. 
d <- left_join(a, b)
left_join(d, q)
```

```{r}
# assignments %>% filter(course_name == "python-osnovy-programmirovaniya") %>% dplyr::select(course_item_name, course_item_type_desc) %>%  group_by(course_item_name) %>% slice(1) #%>% nrow()
```


List of all courses for Appendix:

```{r}
slugs <- data_frame(courses$course_name, courses$course_slug, courses$student_n)
write.csv(slugs, file=paste("/home/vovan/Desktop/data/slugs.csv", sep = ""), row.names = FALSE)
```

Draws:

```{r}
tab <- assignments %>% group_by(course_name) %>%
 mutate(course_item_type_desc = factor(course_item_type_desc), vis_before_attempt_tw_b = ifelse(vis_before_attempt_tw==0, 0, 1), vis_b = ifelse(vis_tw==0, 0, 1), vis_before_attempt_tw_b = factor(vis_before_attempt_tw_b))  %>% group_by(vis_before_attempt_tw_b, course_item_type_desc) %>% summarise(n = n(), prob = sum(first_attempt) / n())
tab
probs <- c(0.7186, 0.73, 0.6616, 0.7459)
tab1 <- cbind(tab, probs) %>% rename(probs = "...5")
tab1

tab1 %>%  ggplot(aes(y = probs, fill = vis_before_attempt_tw_b, x = course_item_type_desc, label= round(probs, 2))) +
  geom_col(stat='identity', position = 'dodge', width=0.7) + 
  labs(x ="Type of an assignment", y = "Probability of Correctness on First Attempt", fill = 'Forum attendance\nbefore attempt') + 
  scale_fill_brewer(palette = "Pastel2", labels = c("No attendance", "Attendance")) +
   geom_text( position = position_dodge(width = 0.7), vjust=1.5,  size=3.5) +
theme_bw() +  
theme(plot.title = element_text(hjust = 0.5))  
```

